MCTS Applied to Co-operative Problems

### 2015-08-01 Report/ceec.tex
Fixed up the door definition to be clearer

\section{The Experiment}
The main premise was to put \gls{mcts} in a situation where it would rely on other AI Agents in order to achieve its objectives, as well as provide a code base for further work with communication between Agents. In order to do this, a problem domain was created.
\subsection{The Problem Domain}
The problem domain is a simple grid world consisting of various objects:
\begin{itemize}
\item{\emph{Floor - } Floors are passable, and are rendered in Grey.}
\item{\emph{Walls -} Walls are impassable, and are fixed in position. \emph{Walls} are rendered in Black.}
\item{\emph{Agents -} Agents are the moving objects that can activate buttons and the goal. \emph{Agents} are rendered in dark Yellow}
\item{\emph{Doors -} Doors are impassable, unless a linked \emph{Button} is currently activated. \emph{Doors} are rendered in Blue whilst closed, and are invisible when open}
\item{\emph{Buttons -} Buttons are passable, and when an \emph{Agent} is on the \emph{Button} it will activate and open the linked \emph{Door}. \emph{Buttons} are rendered in Red}
\item{\emph{Goals -} Goals are passable and reward all \emph{Agents} with a portion of the score. All \emph{Goals} are worth the same amount and the maximum score of $1$ is achieved when every \emph{Agent} has visited every \emph{Goal} at least once. Re-visiting a \emph{Goal} has no effect. \emph{Goals} are rendered in Yellow}
\end{itemize}

>>>>

\section{The Experiment}
The main premise was to put \gls{mcts} in a situation where it would rely on other AI Agents in order to achieve its objectives, as well as provide a code base for further work with communication between Agents. In order to do this, a problem domain was created.
\subsection{The Problem Domain}
The problem domain is a simple grid world consisting of various objects:
\begin{itemize}
\item{\emph{Floor - } Floors are passable, and are rendered in Grey.}
\item{\emph{Walls -} Walls are impassable, and are fixed in position. \emph{Walls} are rendered in Black.}
\item{\emph{Agents -} Agents are the moving objects that can activate buttons and the goal. \emph{Agents} are rendered in dark Yellow}
\item{\emph{Doors -} Doors can either be open or closed. When open, the door is passable. When closed, the door is impassable. Doors are open whilst an \emph{Agent} is activating a linked \emph{Button}. If the \emph{Agent} stops activating the \emph{Button} the \emph{Door} will close. \emph{Doors} are rendered in Blue when closed, and are invisible when open.}
\item{\emph{Buttons -} Buttons are passable, and when an \emph{Agent} is on the \emph{Button} it will activate and open the linked \emph{Door}. \emph{Buttons} are rendered in Red}
\item{\emph{Goals -} Goals are passable and reward all \emph{Agents} with a portion of the score. All \emph{Goals} are worth the same amount and the maximum score of $1$ is achieved when every \emph{Agent} has visited every \emph{Goal} at least once. Re-visiting a \emph{Goal} has no effect. \emph{Goals} are rendered in Yellow}
\end{itemize}
